Seismic parameter estimation and the Canadian crust

### 2013-02-02 paper/draftBP.tex
tiny addition to draft

%% -----------------------------------------------%%
\section{Results}
Canada data

>>>>

%% -----------------------------------------------%%
\section{Results}
Ideas:
Reliability of methods:
  Compare bulk properties garnered from MB to Kan Approach.
  Compare Kan approach values to others in literature
  Canada wide -> Regional

The bulk crustal composition of Canada shows a $frac{V_P}{V_S}$ ratio of $Z$. When compared to the granite - tonalitic - mafic gneiss spectrum this value in very close to the tonalitic gneiss value of $Y$. Compared to other bulk crustal averages this value appears to be X. [Find estimates of bulk averages].
